Title

### 2012-05-21 inc/external_forces/external_forces.tex
Comment on relativistic contributions

>>>>

Further, these analyses are performed in the non-relativistic limit, which is a reasonable approximation for the typical 20-200keV electron energies employed in UED and electron microscopy.  Extension to include relativistic effects is conceptually straightforward using standard transformations between the laboratory and electron pulse reference frames.
